### 2020-11-17 Thesis-Chapter4-Arguments.tex
Add argument that despite hackability, device EA is worth studying

In 2019, Carnegie Mellon assembled an ideologically diverse group of policy and security experts to engage in the kind
of cross-disciplinary debate this thesis advocates. After considering all the technical corners of the situation, their
report goes into detail on why \ac{EA} for domestic law enforcement (i.e., common cases instead of sophisticated
adversaries) focusing on \ac{DAR} in mobile phones using device key escrow requiring physical access is the most
tractable technical case to consider \cite{group_2019}. By now it should be clear why: traditional investigation mixed
with a dose of lawful hacking is best suited for advanced opponents, and device key escrow represents actual progress as
a path towards lower-risk \ac{EA}.

Device key escrow still has a long way to go. There are few proposals, what few there are are high level, and questions
of scaling and administration have not been addressed. However, as \ac{incrementalism}'s Lindblom and even \ac{GCHQ}'s
Levy and Robinson have pointed out, focusing on specific proposals has the opportunity to identify mutually agreeable
solutions---or at least refine the problem understanding enough that the next round of debate can be better informed.

It is this task that we turn to next. The following chapter analyzes one particular device-escrow proposal in moderate
detail, Stefan Savage's ``Lawful Device Access without Mass Surveillance Risk: A Technical Design Discussion''
\cite{savage_lawful_2018}.

% \section{Specific Proposals}
%% NOTE: not worth going into this section. Just describe a few and go straight to one of the most interesting.

% \begin{figure}[h]
%   \centering\CaptionFontSize
%   \includegraphics[width=\linewidth]{arguments/build/comprehensive.proposals.pdf}
%   \caption{EA Proposals}
%   \label{fig-arg-proposals}
% \end{figure}

% % See: committee_decrypting_2018, group_2019, various proposals

>>>>

In 2019, Carnegie Mellon assembled an ideologically diverse group of policy and security experts to engage in the kind
of cross-disciplinary debate this thesis advocates. After considering all the technical corners of the situation, their
report goes into detail on why \ac{EA} for domestic law enforcement (i.e., common cases instead of sophisticated
adversaries) focusing on \ac{DAR} in mobile phones using device key escrow requiring physical access is the most
tractable technical niche to consider \cite{group_2019}. By now it should be clear why: traditional investigation mixed
with a dose of lawful hacking is best suited for advanced opponents, and device key escrow represents actual progress as
a path towards lower-risk \ac{EA} for typical cases.

A strong argument against device key escrow is that device encryption, particularly in mobile phones, may actually pose
the smallest impediment to investigation of any encryption technology. The previously cited report into law enforcement
agencies' ability to access mobile phones clearly demonstrates the current state of affairs: device manufacturers are
losing the exploit arms race, private companies are commodifying the \ac{lawful-hacking} approach for agencies large and
small, and the lack of regulatory strategy has led to pervasive data collection with little oversight
\cite{koepke_2020}. This fact does not undermine the worthiness of research into device-oriented \ac{EA}. First of all,
it underscores the lessons of \mychap{chap-policy}---inaction is an action when facing \acp{wicked-prob}, and in this
case, inaction has led to an undesirable position. Second of all, the current circumstances where device manufacturers
can't keep attackers out is temporary; when law enforcement faces real difficulty again, this issue will immediately
resurface. Law enforcement's anticipation of this is likely why they continue to push for \ac{EA} in spite of present
circumstances. Third of all, regardless of criminal abuse, formalized capability and process can reduce governmental
abuse, which is the clearer threat to privacy and civil liberties.

Despite device key escrow's tractability as a technical niche of \ac{EA}, it still has a long way to go. There are few
proposals, what few there are are high level, and questions of scaling and administration have not been addressed.
However, as \ac{incrementalism}'s Lindblom and even \ac{GCHQ}'s Levy and Robinson have pointed out, focusing on specific
proposals has the opportunity to identify mutually agreeable solutions---or at least refine the problem understanding
enough that the next round of debate can be better informed.

It is this task that we turn to next. The following chapter analyzes one particular device-escrow proposal in detail,
Stefan Savage's ``Lawful Device Access without Mass Surveillance Risk: A Technical Design Discussion''
\cite{savage_lawful_2018}.
